# Assignment 1 - AMS

```{r}
rmarkdown::render("assone.rmd", "html_document")
```

```{r}
install.packages('DescTools')
install.packages('GoFKernel')
install.packages('Ryacas')
install.packages('boot')
install.packages('gmodels') 
install.packages('knitr')
install.packages('mosaic')
install.packages('mosaicCalc')
install.packages('rmarkdown')
install.packages('stats')
install.packages('confintr')

```

```{r}
library(DescTools)
library(GoFKernel)
library(Ryacas)
library(boot)
library(gmodels)
library(knitr)
library(mosaic)
library(mosaicCalc)
library(rmarkdown)
library(stats)
library(confintr)

infinite = 75
```

## Part A

```{r}
F = function(x) (1 - (1/exp((x^2)/8)))
```

### Check whether it is a proper CDF using the limit properties only.

```{r}
x = ysym("x")
lim(F(x), x, +Inf)
```
## Plot it

```{r}
F_mos = makeFun(F(x) ~ x)
plotFun( F_mos(x) ~ x, xlim = c(-2, 10) )
# TODO flaf 2nd part
```

## plot its density for X > 0

```{r}
f = function(x) {}
body(f) = D(body(F), 'x')
curve(f, 0, 10, ylab = "PDF(x)")
```

## compute P(0 < X ≤ 2.3)

```{r}
F(2.3) - F(0)
```

## compute E(X)

As we know E(X) = INTEGER(1 - CDF(X))

```{r}
M = antiD((1-F(x)) ~ x)
mu = M(+Inf) - M(0)
mu
```

## compute VAR(X)

```{r}
MM = antiD((x*f(x)*(x)) ~ x)
ex2 = MM(infinite) - MM(0)
ex2 - (mu*mu)
```

## compute the median

```{r}
F_inv = inverse(F, lower=0, upper=infinite)
F_inv(0.5)
```

## Part B

```{r}
df = read.csv(file = 'CustomerCare.csv')
dt = subset(df , columns=c('Education','Rating_price','Rating_quality'))
```
Consider the CustomerCare.csv dataset on rating about a new product (columns Rating_price and Rating_quality). After considering the variable Education as group variable:

## Perform a MANOVA test to determine if there are differences in the mean vectors ofthe ratings in the education level groups

```{r}

```

## Perform univariate ANOVA tests on each variable

```{r}
```

## Compare and comment on results

```{r}

```

Hints: for (i) you might use the manova R function; for (ii) you might use the aov()function

## Part C

```{r}
df = read.csv(file = 'CustomerCare.csv')

```

### Consider the CustomerCare.csv dataset on rating about a new product (column Rating_price). Implement the classical bootstrap to estimate the (95%) confidence intervals of the population Pearson's correlation coefficient between rating and Age. Compare with the Fisher transform method. Implement an iterative procedure and a package procedure (for example using boot)

```{r}
dt = subset(df, select = c("Rating_price","Age"))
N = length(dt[,1])
X = df$Age
Y = df$Rating_price
```

```{r}
## iterative procedure

n_iter = 1000
corrs = rep(NULL, n_iter)

for (i in 1:n_iter){
    indexes = as.matrix(sample(1:N, sqrt(N)), replace=TRUE)
    corrs[i] = cor(X[indexes], Y[indexes])
}

hist(corrs)
sbs = round(ci(corrs, confidence=0.95), 3)
sbs
```
### The sampling distribution of Pearson\'s r is not normally distributed. Fisher developed a transformation now called "Fisher's z-transformation" that converts Pearson's r to the normally distributed variable z. The formula for the transformation is:
$$z_r = tanh^{-1}(r) = \frac{1}{2}log\left ( \frac{1+r}{1-r}\right )$$

```{r}
## LIBRARY
foo = function(data, indexes) {
    return(cor(data[indexes,1],data[indexes,2]))
}

results = boot(dt, foo, R = n_iter, stype = 'i' )
results
```

```{r}
tmp1 = ci_cor(X, Y, method = "pearson", type = "normal")
zs = FisherZ(cor(X,Y))
zs

tmp2 = ci_cor(X, Y, method = "pearson", type = "bootstrap")
```

```{r}

est = ci(zs, confidence=0.95)
pkg = round(FisherZInv(est), 3)
pkg
```

### Plot the confidence intervals to visually compare the results

```{r}
data = data.frame(
    x = c(1:2),
    y = c(sbs['Estimate'], pkg['Estimate']),
    lower = c(sbs['CI lower'], pkg['CI lower']),
    upper = c(sbs['CI upper'], pkg['CI upper'])
)

#install.packages("plotrix")
library("plotrix")

plotCI(x = data$x,
       y = data$y,
       li = data$lower,
       ui = data$upper)
```

### Compute the (95%) boostrap confidence interval for Y/X

```{r}
# TODO
```

### Comment on results.


NOTE: you may extend that example including the use of other bootstrap R packages you may find.