---
title: "Assignment 1"
output: pdf_document
---

*Part b*

For this second task a two-way Manova and two Anova tests are going to be performed in order to perform a multivariate and two univariate analysis of variance.
The aim is to test if the variables regarding the ratings given to price and to quality of products by the customers are affected by the level of education of the customers.


```{r}
setwd("~/Desktop/advanced multivariate statistics/assignment 1")

dataset = read.csv("CustomerCare.csv", sep = ";")

dataset
```

Given that the Manova and Anova test require multivariate normality, a Shapiro-Wilk test is performed before proceeding with the analysis.


```{r}

# check for normality

sub_data <- cbind(dataset$Rating_price, dataset$Rating_quality, dataset$Education)
data.frame(sub_data)

shapiro.test(sub_data)

```



This tests results in a p-value < 0.05, multivariate normality is confirmed. 
The Manova and Anova tests can be performed.


```{r}
# TWO WAY MANOVA

price <- dataset$Rating_price
quality <- dataset$Rating_quality
dep_variables <- cbind(price, quality)

# MANOVA test
res.man <- manova(dep_variables ~ Education, data = dataset)
summary(res.man)
```

Given a large p-value >0.05, it cannot be inferred that Education level has an influence on the ratings that customers give to the price and to the quality of the new product.


```{r}
#ANOVA PRICE

# Compute the analysis of variance
res.aov <- aov(Rating_price ~ Education, data = dataset)
# Summary of the analysis
summary(res.aov)
```


```{r}
#ANOVA RATING

# Compute the analysis of variance
res.aov <- aov(Rating_quality ~ Education, data = dataset)
# Summary of the analysis
summary(res.aov)
```


....


*Part c*

**PEARSON**

```{r}

set.seed(42)

# bootstrap by hand

price <- dataset$Rating_price
age <- dataset$Age

N=length(dataset[,1])
sample_boot <- cbind(price, age)
data.frame(sample_boot)

B=500

boot_reps <- vector ("numeric", length = B)

for (b in 1:B) {
  boot_indexes <-as.matrix(sample(1:N, 100), replace=TRUE)
  price_values <- price[boot_indexes]
  age_values <- age[boot_indexes]
  cor.test(price_values, age_values, alternative = "two.sided", method = "pearson", exact = NULL, conf.level = 0.95, continuity = FALSE)
r <- cor.test(price_values,age_values)$estimate
  boot_reps[b]<-r
}

mean_bootpearson<-mean(boot_reps)
se_boot<-(sum((boot_reps-mean_bootpearson)^2)/(B-1))^0.5
se_boot
mu_1 <- mean_bootpearson

upper_1 <- mean_bootpearson + (0.95)*(sd(boot_reps))/sqrt(B)
lower_1 <- mean_bootpearson - (0.95)*(sd(boot_reps))/sqrt(B)

conf_1 <- c(lower_1, mu_1, upper_1)

conf_1

```



```{r}

# bootstrap with library

library(boot)

B=500

data_boot <- subset(dataset, select = c("Rating_price", "Age"))

get.corr<-function(data,indices){
  data <- data[indices,]
  price <- data[,1]
  age <- data[,2]
  cor.test(price, age, alternative = "two.sided", method = "pearson", exact = NULL, conf.level = 0.95, continuity = FALSE)
r <- cor.test(price, age)$estimate
  return(r)
}

boot.output<-boot(data_boot,get.corr,R=B, stype = "i")
boot.output

mu_2 <- boot.output$t0

std <- boot.output$t



upper_2 <- mu_2 + (0.95)*(sd(std))/sqrt(B)
lower_2 <- mu_2 - (0.95)*(sd(std))/sqrt(B)

conf_2 <- c(lower_2, mu_2, upper_2)

conf_2



 

```



**FISHER**



```{r}

library(DescTools)

# bootstrap by hand

price <- dataset$Rating_price
age <- dataset$Age

N=length(dataset[,1])
sample_boot <- cbind(price, age)
data.frame(sample_boot)

B=500

boot_reps <- vector ("numeric", length = B)

for (b in 1:B) {
  boot_indexes <-as.matrix(sample(1:N, 100), replace=TRUE)
  price_values <- price[boot_indexes]
  age_values <- age[boot_indexes]
  cor.test(price_values, age_values, alternative = "two.sided", method = "pearson", exact = NULL, conf.level = 0.95, continuity = FALSE)
r <- cor.test(price_values,age_values)$estimate
z <- FisherZ(r)

  boot_reps[b]<-z
}

mean_bootpearson<-mean(boot_reps)
se_boot<-(sum((boot_reps-mean_bootpearson)^2)/(B-1))^0.5
se_boot
mu_3 <- mean_bootpearson

upper_3 <- mu_3 + (1.96)*(1/sqrt(N-3))
lower_3 <- mu_3 - (1.96)*(1/sqrt(N-3))

conf_3 <- c(lower_3, mu_3, upper_3)
FisherZInv(conf_3)






```
```{r}

#bootsrtap with library

library(boot)

B=500

data_boot <- subset(dataset, select = c("Rating_price", "Age"))

get.corr<-function(data,indices){
  data <- data[indices,]
  price <- data[,1]
  age <- data[,2]
  cor.test(price, age, alternative = "two.sided", method = "pearson", exact = NULL, conf.level = 0.95, continuity = FALSE)
r <- cor.test(price, age)$estimate
z <- FisherZ(r)
  return(z)
}

boot.output<-boot(data_boot,get.corr,R=B, stype = "i")
boot.output

mu_4 <- boot.output$t0

upper_4 <- mu_4 + (1.96)*(1/sqrt(N-3))
lower_4 <- mu_4 - (1.96)*(1/sqrt(N-3))



conf_4 <- c(lower_4, mu_4, upper_4)
FisherZInv(conf_4)


```

```{r}
library(DescTools)

price <- dataset$Rating_price
age <- dataset$Age

cor.test(price, age, alternative = "two.sided", method = "pearson", exact = NULL, conf.level = 0.95, continuity = FALSE)
r <- cor.test(price,age)$estimate
mu_5 <- FisherZ(r)

upper_5 <- mu_5 + (1.96)*(1/sqrt(N-3))
lower_5 <- mu_5 - (1.96)*(1/sqrt(N-3))

conf_5 <- c(lower_5, mu_5, upper_5)
FisherZInv(conf_5)
```



```{r}

#install.packages("plotrix")
library("plotrix")

data <- data.frame(x=1:5,
                   y= c(mu_1, mu_2, mu_3, mu_4, mu_5),
                   lower = c(lower_1, lower_2, lower_3, lower_4, lower_5),
                   upper = c(upper_1, upper_2, upper_3, upper_4, upper_5))

plotCI(x=data$x,
       y=data$y,
       li=data$lower,
       ui=data$upper)


```
```{r}
print(conf_1)
print(conf_2)
print(conf_3)
print(conf_4)
print(conf_5)
```

conclusione: bootstrap è meglio di fisher 
rating price e age sono very weakly positively correlated







```{r}
Y <- dataset$Rating_price
X <- dataset$Rating_quality

library(boot)

B=500

data_boot <- subset(dataset, select = c("Rating_quality", "Rating_price"))

get.ratio<-function(data,indices){
  data <- data[indices,]
  quality <- data[,1]
  price <- data[,2]
  q = sum(price)/sum(quality)
  return(q)
}

boot.output<-boot(data_boot,get.ratio,R=B, stype = "i")
boot.output


mu <- boot.output$t0

std <- boot.output$t



upper_bound <- mu + (0.95)*(sd(std))/sqrt(B)
lower_bound <- mu - (0.95)*(sd(std))/sqrt(B)

conf_6 <- c(lower_bound, mu, upper_bound)

conf_6




```
rapporto tra due somme non normale

Bootstrap per normalizzare

conf int per dimostrare che il ratio sia >1 

People tend to give more positive ratings to price than to quality.


